\newpage

\appendix

\chapter{Game Specification}

The Game will begin with a Start menu to choose the opponent as either a computer or another person.
Against a computer the player will always have the black chips, while pass and play chip ownership will be determined by who plays which chips.

Regardless of the type of play, the UI will prompt the Game to
generate the board with the appropriate chip starting positions.
Black will start with 2, 5, 3, 5 chips at points 1, 12, 17, 19,
while red will start with 2, 5, 3, 5 chips at points 24, 13, 8 , 6.

After the Game has been initialized, the first thing to be done will
be the roll to determine who will move first. Both players will roll a
single die and the person who rolls highest will be the first to move.
If both players roll the same number, then both players will reroll their die.
When the first to move has been decided, Game will generate a list of valid
moves for that player (by chip colour).

Valid moves will be highlighted on the UI for the player's indication for
which chips can be moved. A player can then move only highlighted chips.
After every move the list of possible moves will be refreshed.
If a player has no chips then that person's turn ends.

It will then be the other player's turn. They will have to roll the dice.
Rolling doubles, doubles the number of uses for the dice, so the person can
move 4 times instead of 2. They will then be prompted to move.

This will continue until 1 person has born off all their chips.
